Discrete Quantum Theories and Computing

### 2018-11-12 dissertation.tex
dissertation.lyx "2.2 Quantum Probability" Updating, and then put TODOs so that I can wrap up and send to Andy...

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
Given a finite sample space~$\Omega$, and its power set $2^{\Omega}$
as the classical event space, a classical probability measure $\mu$
describe how likely every event~$E$ could happen by mapping $E$
to a number $\mu\left(E\right)\in\left[0,1\right]$.

is a function subject to the following constraints: $\mu\left(\emptyset\right)=0$,
$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

In the quantum case, the events of interest are specified by \emph{projection
operators} $P$ satisfying the condition $P^{2}=P$. These include
the empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\Phi}$ where $\ket{\Phi}$ is a pure
quantum state (an element of a Hilbert space $\mathcal{H}$), sums
of \emph{orthogonal} projectors~$P_{0}$ and~$P_{1}$ with $P_{0}P_{1}=\mathbb{0}$,
and products of \emph{commuting} projectors $P_{0}$ and~$P_{1}$
with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
using a probability measure $\mu:\events\rightarrow\left[0,1\right]$,
where $\events$ is the set of all events, (i.e., projectors on a
given Hilbert space), subject to the following constraints:
\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
\end{align}
and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
assignment for every projector $P$, we can define the expectation
value of an observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
as \cite{544199,Jaeger2007}: 
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
\end{equation}
where the subscript $\mu$ might be omitted if it is clear according
to the context.

>>>>

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
Given a finite sample space~$\Omega$ representing all possible outcomes,
and its power set $2^{\Omega}$ as the classical event space, a classical
probability measure~$\mu$ maps an event~$E$ to a number $\mu\left(E\right)\in\left[0,1\right]$
specifying how likely one of the outcome~$\omega\in E$ actually
happens. To maintain the coherence, we want $\mu$ subject to the
following constraints: $\mu\left(\emptyset\right)=0$, $\mu\left(\Omega\right)=1$,
$\mu\left(\overline{E}\right)=1-\mu\left(E\right)$, and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

In the quantum case, the events of interest are specified by \emph{projection
operators} $P$ satisfying the condition $P^{2}=P$. These include
the empty projector~$\mathbb{0}$, the identity projector~$\mathbb{1}$,
projectors of the form $\proj{\Phi}$ where $\ket{\Phi}$ is a pure
quantum state (an element of a Hilbert space $\mathcal{H}$), sums
of \emph{orthogonal} projectors~$P_{0}$ and~$P_{1}$ with $P_{0}P_{1}=\mathbb{0}$,
and products of \emph{commuting} projectors $P_{0}$ and~$P_{1}$
with $P_{0}P_{1}=P_{1}P_{0}$. In a quantum probability space \cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010,Abramsky2012},
the set of all events is the set of all projectors on a given Hilbert
space denoted by $\events$. After the measurement, if the system
transits to a state $\ket{\Phi}$ and we call an event $P\in\events$
happen when .

each event~$P_{i}$ is mapped to a probability~$\mu\left(P_{i}\right)$
using a probability measure $\mu:\events\rightarrow\left[0,1\right]$
subject to the following constraints:
\begin{align}
\mu\left(\mathbb{0}\right) & =0\,, & \mu\left(\mathbb{1}\right) & =1\,, & \mu\left(\mathbb{1}-P\right) & =1-\mu\left(P\right)\,,\label{eq:QuantumProbability}
\end{align}
and for each pair of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}
Given a Hilbert space $\mathcal{H}$ of dimension $D$ and a probability
assignment for every projector $P$, we can define the expectation
value of an observable~$\mathbf{O}$ having spectral decomposition
$\mathbf{O}=\sum_{i=0}^{D-1}\lambda_{i}P_{i}$, with eigenvalues $\lambda_{i}\in\mathbb{R}$,
as \cite{544199,Jaeger2007}: 
\begin{equation}
\expval{\mathbf{O}}_{\mu}=\sum_{i=0}^{D-1}\lambda_{i}\mu\left(P_{i}\right)\,,\label{eq:quantum-expectation}
\end{equation}
where the subscript $\mu$ might be omitted if it is clear according
to the context.
